Fail Faster

### 2025-03-05 paper/paper.tex
further skeleton tech section

>>>>

% let rec genpick n ws =
% match ws with
% | [] -> { rand_gen = fun ~size_c:_ ~random_c:_ -> Codecps.return .< failwith "Fell of the end of pick list" >. }
% | (k,g) :: ws' ->
%       { rand_gen = 
%         fun ~size_c ~random_c ->
%           Codecps.bind (Codecps.split_bool .< Float.compare .~(v2c n) .~(v2c k) <= 0 >.) (fun leq ->
%             if leq then
%               g.rand_gen ~size_c ~random_c
%             else
%               Codecps.bind (Codecps.let_insertv .< .~(v2c n) -. .~(v2c k) >.) @@ fun n' ->
%               (* let%bind n' =  in *)
%               (genpick n' ws').rand_gen ~size_c ~random_c
%         )
%       }

\begin{lstlisting}
  let weighted_union (weighted_elts : (float code * 'a code) list) : 'a t =
    let sum_code = List.foldr _ in
    let go (rc : int code) (weighted_elts : (float code * 'a code) list) : 'a code =
      match weighted_elts with
      | [] -> .< failwith "Error" >.
      | (wc,xc) :: elts' ->
        .<
          if .~rc <= .~wc then .~xc
          else
            let r' = .~rc - .~wc in
            .~(go .<r'>. elts')
        >.

    fun size_c random_c ->
      .<
        let sum = .~sum_code in
        let r = SR.int .~random_c 0 sum in
        .~(go .<r>. gwcs)
      >.
\end{lstlisting}

Then, if we write

\begin{lstlisting}
let grades : charBq.t gen = to_bq (
  weighted_union [
    (.<3.0>., 'a');
    (.<2.0>., 'b');
    (.<1.0>., 'c');
  ]
)
===
Bq.create (
  fun size random ->
    let sum = 3.0 + 2.0 + 1.0 in
    let r = SR.int random 0 sum in
    if r <= 3.0 then 'a'
    else
      let r' = r - 3.0 in
      if r' <= 2.0 then 'b'
      else
        let r'' = r' - 2.0 in
        if r'' <= 1.0 then 'c'
        else
          failwith "Error"
)
\end{lstlisting}

\subsection{``The Trick'' and Effect Ordering}
